BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-16 tex/1-intro.tex
Into on RSS almost done, some issues to compile w latexmk

Blogs disappear every day. Losing data is obviously undesirable, but even more so when this data has historic, politic or scientific value. In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation. Yet, blogs are an important part of today's web: the WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}. Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests. \cite{nahedeltantawy2012}\comment{not sure where to put this one}. The need for preservation for this volatile communication medium is today a necessity.\comment{Do you have a better closing sentence?}

Among the challenges in developing a blog archiving software is* providing an automatic web crawler to \TODO{better keyword} traverse blogs and accurately extract their content. The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary. The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents. Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.

A key characteristic of blogs which differentiates them from regular website is their association with web feeds. Their primary use is to provide a uniform subscription mechanism, allowing users to keep track of the latest updates without the need periodically visit the blogs of interest.

push pull model
usefully in many ways,

-> we can use web feed to build content extraction algorithm that, as we will see, outperform the more generic approaches that not rely on webfeed.

>>>>

Blogs disappear every day. Losing data is obviously undesirable, but even more so when this data has historic, politic or scientific value. In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation. Yet, blogs are an important part of today's web: the WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}. Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests. \cite{nahedeltantawy2012}\comment{Not sure where to put this one...}. The need for preservation of this volatile communication medium is today a necessity.\comment{Do you have a better closing sentence?}

Among the challenges in developing a blog archiving software is* providing a web crawler capable of efficiently traversing blogs to harvest their content. The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary. The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents. Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.

A key characteristic of blogs which differentiates them from regular website is their association with web feeds. Their primary use is to provide a uniform subscription mechanism, allowing users to keep track of the latest updates without the need to visit their blogs of interest. The two competing web feed technologies, Atom and RSS, use **the pull model**. Concretely, a web feed is a XML file containing links to the last posts of blog, along with abstracts or the full texts of articles and the associated metadate.

usefully in many ways,

-> we can use web feed to build content extraction algorithm that, as we will see, outperform the more generic approaches that not rely on web feed.

### 2014-01-16 tex/3-algorithms.tex
up
Into on RSS almost done, some issues to compile w latexmk

This section explains in detail the algorithm we developed to extract blog post articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of throughout a blog. Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.

@@

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, its title, authors and publication date. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

>>>>

This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of throughout a blog. Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.

@@

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date. We call these fields \emph{targets} as they constitute the data our crawler aims to extract. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.
